Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-24 paper/paper.Rmd
Rename section custom rsmp to "Custom and grouped resampling"
rephrase a bit

### Group-level resampling

@@

### Custom (fixed) Resampling --- mlr3

<!--JM: you might want to delete the FIXME-->
Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

@@

Most often multiple spatial partitioning methods can be used for a dataset.
It is recommended (required) that one familiarizes themselves with multiple methods and decide which method to choose based on the specific characteristics of the dataset at hand and the prediction purpose of the fitted model, i.e. for which areas/zones a model should make predictions for.
There are various variables influencing the partitioning method choice for an environmental dataset:

>>>>

### Group-level resampling {#sec:group-level}

@@

### Custom and grouped resampling --- mlr3

<!--JM: you might want to delete the FIXME-->
Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version 0.12.0 FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
This partitioning concept is also ften referred to as "grouped resampling" and should not be mistaken with "group-level resampling" (section \@ref(sec:group-level)), which inherits additional aggregation of groups at the partition level.
Each level of the factor vector will result in one partition.
Alternatively to supplying an external factor vector, the name of a feature (type `character`) present within the task can be supplied via argument `col`.

@@

Most often multiple spatial partitioning methods can be used for a dataset.
It is recommended (required) to make oneself familiar with the available methods and to decide on one based on the specific characteristics of the dataset at hand and the prediction purpose of the fitted model.
The prediction purpose is the model's ability for which areas or zones it actually can make predictions.
For example, ...
<!--JM: maybe refer back to the crop example of the intro to make the point better comprehensible than just giving the mere theory-->

There are various variables influencing the partitioning method choice for an environmental dataset:
